Are mental properties supervenient on brain properties?

### 2010-08-17 PLoS_ONE/resubmission/supervenience_old.tex
got reviews back from plos one, rearranged a bit and started making edits

While the above theorem is of potential theoretical interest, because the arguments rest on knowing $F_{BM}$ and $g^*$, which are typically unknown, they are pragmatically useless.  However, both $F_{BM}$ and $g^*$ could be estimated from data.  Let $(b_1,m_1), (b_2,m_2), \ldots, (b_n,m_n)$ be random samples taking their values in $\mB \times \mM$, independently and identically distributed according to model $F_{BM}$.  Generalizing the concept of a classifier $g$ to allow incorporation of training data, consider $g_n:\mB \times (\mB \times \mM)^n \mapsto \mM$ which takes as input an observed brain connectivity structure $b$ and $n$ training pairs $\tr{\mc{T}_n=}\{(b_1,m_1),\cdots,(b_n,m_n)\}$ and produces a classification $g_n(b;\tr{\mc{T}_n})=\mh{m}$.  Misclassification rate for this classifier will therefore be a random variable, because the training data $\mc{T}_n$ are random samples.  Therefore, instead of calculating misclassification rate for $g_n$, we compute the expected misclassification rate: % as the expectation of $\PP[g_n(B)=M | \mc{T}_n]$ over all possible training data corpuses:
\begin{align}
\EE[L_{F}(g_n)] = \EE[P_{F}[g_n(B;\tr{\mc{T}_n}) \neq M|\tr{\mc{T}_n}]] = \int \PP_F[g_n(B)=M | \mc{T}_n] \PP[\mc{T}_n] d\mc{T}_n.
\end{align}
Unfortunately, in practice, computing $\EE[L_F(g_n)]$, requires integrating over all possible training data corpuses, and by definition, we only have access to a single training data corpus.  We therefore define ``hold out'' misclassification performance:
\begin{align}
\EE[L_F(g_n)] %= \int \PP_F[g_n(B)=M | \mc{T}_{n'-n}] \PP[\mc{T}_{n'-n}] d\mc{T}_{n'n} \nonumber \\ 
&\approx  \hL^{n'}_{F}(g_n) = \sum_{\mc{T}_{n-n'}} \PP_F[g_n(B)=M | \mc{T}_{n-n'}] \PP[\mc{T}_{n-n'}],
\end{align}
where $n'<n$ is the number of held-out training samples, and the sum is taken over a sufficiently large number of subsets, $\mc{T}_{n-n'}$, such that $\hL^{n'}_F(g_n)$ converges.   $n' \hL^{n'}_{F}(g_n)$ is the expected number of misclassified minds.  Simplifying further, assuming no sum, rather, just one ``hold-out'' set, then $n' \hL^{n'}_{F}(g_n)$ and has a binomial distribution, because for any of the $n'$ held-out samples, the classifier could be either correct or incorrect, thus $n' \hL^{n'}_{F}(g_n) \sim \text{Binomial}(n',L_{F}(g_n))$.

@@

Importantly, the utility of any statistical test depends both on the p-value, the probability of obtaining a test statistic at least as extreme as the observed value (under the assumed model), and its power, the probability that the test will reject a false null hypothesis (in other words, the probability that it will not make a Type II error).  Ideally, the power of this test would go to unity, as $n,n' \rightarrow \infty$.  A sufficient condition for power to approach unity is that $g_n$ is a \emph{consistent} classifier.  A classifier is consistent if and only if its expected misclassification rate converges to the Bayes optimal limit with sufficient data, that is $\EE[L_F(g_n)] \conv L_F(g^*)$ as $n\conv \infty$. As the notation suggests, consistency of a classifier is a function of the true model, $F$.  Without any prior knowledge of what the model might be, one desires a \emph{universally consistent} classifier, that is a classifier that is consistent for all $F \in \mc{F}$.

@@

In 1977, Stone proved that a certain collection of $k_n$ nearest neighbor algorithms is universally consistent, assuming $b$ was a random $d$-dimensional vector $\mc{B} \subseteq \Real^d$ \cite{Stone77} (see Appendix \ref{app:knn} for an explanation of $k_n$ nearest neighbor algorithms, and constraints to ensure universal consistency) (since then, other algorithms have also been shown to be universally consistent, most notably neural networks \cite{Cybenko89}).  This beautiful result would be directly applicable to mind-brain supervenience, if we were satisfied representing brains by random vectors.  However, brains are rich with structure, and therefore, other, more sophisticated data structures can better capture aspects of the brain that many of us believe to be true. Therefore, in the next section, we introduce the concept of a \emph{brain-graph}, which can have a much richer structure than a vector.  We then generalize the $k_n$ nearest neighbor algorithm to operate in this domain, and extend the universal consistency proof as well.

@@

In 1891, H Waldeyer-Hartz first formally proposed the ``neuron doctrine'' \cite{Waldeyer-Hartz1891}, which states that the nervous system is a complex \emph{network} of ``neurons'' (a term invented in the above review), largely based on Ramon y Cajal's work using the Golgi stain \cite{Finger01}.  This doctrine has been central to much of the development of neuroscience and artificial intelligence for over 100 years, including the development of neural network theory \cite{Bishop95} and cognitive science \cite{McClellandRumelhart86}.  In parallel with the development and refinement of concepts of how collections of neurons may collectively operate to subserve various brain functions, a simultaneous development has taken place in the statistical analysis of networks, or graphs \cite{Bollobas, otherbook}.  We therefore propose to represent the brain as a random graph, where nodes represent neurons and edges represent synapses.  Formally, a brain-graph $G=(V,A)$ is characterized by a set of vertices (or nodes), $\{V_i\} = \{V_1,\ldots, V_n\}$, where $n$ is the number of neurons, and arcs (or edges) $\{A_{ij}\}$, where $A_{ij}$ represents the synapse from neuron $V_j$ to $V_i$. For simplicity (to be generalized below), assume that brain-graphs are simple graphs, meaning that (i) there are no self loops (no autapses, or self-connections), (ii) all edges are binary, meaning that $a_{ij} \in \{0,1\}$, and (iii) all edges are symmetric, that is, $a_{ij}=a_{ji}$.  Further assuming that the vertices are \emph{labeled}, meaning that there is a known one-to-one mapping

from vertex $V_i$ in

Formally, assume that each brains, $b \in \mc{B}$

>>>>

While the above theorem is of potential theoretical interest, because the arguments rest on knowing $F_{BM}$ and $g^*$, which are typically unknown, they are pragmatically useless.  However, both $F_{BM}$ and $g^*$ could be estimated from data.  Let $(b_1,m_1), (b_2,m_2), \ldots, (b_n,m_n)$ be random samples taking their values in $\mB \times \mM$, independently and identically distributed according to model $F_{BM}$.  Generalizing the concept of a classifier $g$ to allow incorporation of training data, consider $g_n:\mB \times (\mB \times \mM)^n \mapsto \mM$ which takes as input an observed brain connectivity structure $b$ and $n$ training pairs $\tr{\mc{T}_n=}\{(b_1,m_1),\cdots,(b_n,m_n)\}$ and produces a classification $g_n(b;\tr{\mc{T}_n})=\mh{m}$.  Misclassification rate for this classifier will therefore be a random variable, because the training data $\mc{T}_n$ are random samples.  Therefore, instead of calculating misclassification rate for $g_n$, we compute the expected misclassification rate: % as the expectation of $\PP[g_n(B)=M | \mc{T}_n]$ over all possible training data corpuses:
\begin{align}
\EE[L_{F}(g_n)] = \EE[P_{F}[g_n(B;\tr{\mc{T}_n}) \neq M|\tr{\mc{T}_n}]] = \int \PP_F[g_n(B)=M | \mc{T}_n] \PP[\mc{T}_n] d\mc{T}_n.
\end{align}
Unfortunately, in practice, computing $\EE[L_F(g_n)]$, requires integrating over all possible training data corpuses, and by definition, we only have access to a single training data corpus.  We therefore define ``hold out'' misclassification performance:
\begin{align}
\EE[L_F(g_n)] %= \int \PP_F[g_n(B)=M | \mc{T}_{n'-n}] \PP[\mc{T}_{n'-n}] d\mc{T}_{n'n} \nonumber \\ 
&\approx  \hL^{n'}_{F}(g_n) = \sum_{\mc{T}_{n-n'}} \PP_F[g_n(B)=M | \mc{T}_{n-n'}] \PP[\mc{T}_{n-n'}],
\end{align}
where $n'<n$ is the number of held-out training samples, and the sum is taken over a sufficiently large number of subsets, $\mc{T}_{n-n'}$, such that $\hL^{n'}_F(g_n)$ converges.   $n' \hL^{n'}_{F}(g_n)$ is the expected number of misclassified minds, and has a binomial distribution, because for any of the $n'$ held-out samples, the classifier could be either correct or incorrect, thus $n' \hL^{n'}_{F}(g_n) \sim \text{Binomial}(n',L_{F}(g_n))$.

@@

Importantly, the utility of any statistical test depends both on the p-value, the probability of obtaining a test statistic at least as extreme as the observed value, and its power, the probability that the test will reject a false null hypothesis (in other words, the probability that it will not make a Type II error).  Ideally, the power of this test would go to unity, as $n,n' \rightarrow \infty$.  A sufficient condition for power to approach unity is that $g_n$ is a \emph{consistent} classifier.  A classifier is consistent if and only if its expected misclassification rate converges to the Bayes optimal limit with sufficient data, that is $\EE[L_F(g_n)] \conv L_F(g^*)$ as $n\conv \infty$. As the notation suggests, consistency of a classifier is a function of the true model, $F$.  Without any prior knowledge of what the model might be, one desires a \emph{universally consistent} classifier, that is a classifier that is consistent for all $F \in \mc{F}$.

@@

In 1977, Stone proved that a certain collection of $k_n$ nearest neighbor algorithms is universally consistent, assuming $b$ was a random $d$-dimensional vector $\mc{B} \subseteq \Real^d$ \cite{Stone77} (see Appendix \ref{app:knn} for an explanation of $k_n$ nearest neighbor algorithms, and constraints to ensure universal consistency).  This beautiful result would be directly applicable to mind-brain supervenience, if we were satisfied representing brains by random vectors.  However, brains are rich with structure, and therefore, other, more sophisticated data structures can better capture aspects of the brain that many of us believe to be true. Therefore, in the next section, we introduce the concept of a \emph{brain-graph}, which can have a much richer structure than a vector.  We then generalize the $k_n$ nearest neighbor algorithm to operate in this domain, and extend the universal consistency proof as well.

@@

In 1891, H Waldeyer-Hartz first formally proposed the ``neuron doctrine'' \cite{Waldeyer-Hartz1891}, which states that the nervous system is a complex \emph{network} of ``neurons'' (a term invented in the above review), largely based on Ramon y Cajal's work using the Golgi stain \cite{Finger01}.  This doctrine has been central to much of the development of neuroscience and artificial intelligence for over 100 years.

### 2010-08-17 PNAS/PNAS_submission.tex
got reviews back from plos one, rearranged a bit and started making edits

\author{Joshua T. Vogelstein\affil{1}{Johns Hopkins University, Baltimore, MD}, 
R. Jacob Vogelstein\affil{1}{}, 
Carey E. Priebe\affil{1}{}}

@@

\begin{acknowledgments}
The authors would like to acknowledge helpful discussions with J Lande and B Vogelstein.
\end{acknowledgments}

@@

\begin{thebibliography}{26}

\bibitem{Plato97}
Plato.
\newblock {\em Plato: complete works}.
\newblock Hackett Pub Co,  (1997).

\bibitem{Descartes1641}
Descartes, R.
\newblock {\em Meditationes de prima philosophia}.
\newblock  (1641).

\bibitem{Davidson70}
Davidson, D.
\newblock {\em Experience and Theory}, chapter Mental Events.
\newblock Duckworth (1970).

\bibitem{SpornsKotter05}
Sporns, O., Tononi, G., and Kotter, R.
\newblock {\em PLoS Computational Biology}{ \bf 1}(4), e42 (2005).

\bibitem{LichtmanSanes08}
Lichtman, J.~W., Livet, J., and Sanes, J.~R.
\newblock {\em Nat Rev Neurosci}{ \bf 9}(6), 417--422 Jun  (2008).

\bibitem{Seung09}
Seung, H.
\newblock {\em Neuron}{ \bf 62}(1), 17--29 (2009).

\bibitem{Kim95}
Kim, J.
\newblock {\em Phiilosophy of Mind}.
\newblock Westview Press, second edition,  (2005).

\bibitem{DGL96}
Devroye, L., Gy{\"o}rfi, L., and Lugosi, G.
\newblock {\em {A Probabilistic Theory of Pattern Recognition}}.
\newblock Springer,  (1996).

\bibitem{Devroye83}
Devroye, L.
\newblock {\em Probability Theory and Related Fields}{ \bf 62}(4), 475--483
  (1983).

\bibitem{Popper}
Popper, K.
\newblock { \bf } (1959).

\bibitem{WhiteBrenner86}
White, J., Southgate, E., Thomson, J.~N., and Brenner, S.
\newblock {\em Philosophical Transactions of Royal Society London. Series B,
  Biological Sciences}{ \bf 314}(1165), 1--340 (1986).

\bibitem{DenkHorstmann04}
W.~Denk, W. and Horstmann, H.
\newblock {\em PLOS Biol.}{ \bf 2}, e329 (2004).

\bibitem{BriggmanDenk06}
Briggman, K. and Denk, W.
\newblock {\em Current opinion in neurobiology}{ \bf 16}(5), 562--570 (2006).

\bibitem{MackeBorst08}
Macke, J.~H., Maack, N., Gupta, R., Denk, W., Schölkopf, B., and Borst, A.
\newblock {\em J Neurosci Methods}{ \bf 167}(2), 349--357 Jan  (2008).

\bibitem{Mishchenko09}
Mishchenko, Y.
\newblock {\em J Neurosci Methods}{ \bf 176}(2), 276--289 Jan  (2009).

\bibitem{LuLichtman09}
Lu, J., Fiala, J.~C., and Lichtman, J.~W.
\newblock {\em PLoS ONE}{ \bf 4}(5), e5655 05  (2009).

\bibitem{HornJohnson90}
Horn, R. and Johnson, C.
\newblock {\em {Matrix analysis}}.
\newblock Cambridge Univ Pr,  (1990).

\bibitem{ConroyLouis97}
Conroy, J.~M., Kratzer, S.~G., and Podrazik, L.~J.
\newblock In {\em Society for Industrial and Applied Mathematics},  (1997).

\bibitem{ZaslavskiyVert08}
Zaslavskiy, M., Bach, F., and Vert, J.
\newblock {\em IEEE Transactions on Pattern Analysis and Machine Intelligence}{
  \bf 31}, 2227--2242 (2008).

\bibitem{Durbin87}
Durbin, R.~M.
\newblock {\em Studies on the Development and Organisation of the Nervous
  System of Caenorhabditis elegans}.
\newblock PhD thesis, University of Cambridge,  (1987).

\bibitem{deBonoMaricq05}
de~Bono, M. and Maricq, A.~V.
\newblock {\em Annu Rev Neurosci}{ \bf 28}, 451--501 (2005).

\bibitem{VarshneyChklovskii09}
Varshney, L., Chen, B., Paniagua, E., Hall, D., and Chklovskii, D.
\newblock {\em ArXiv}{ \bf } (2009).

\bibitem{ChalasaniBargmann07}
Chalasani, S.~H., Chronis, N., Tsunozaki, M., Gray, J.~M., Ramot, D., Goodman,
  M.~B., and Bargmann, C.~I.
\newblock {\em Nature}{ \bf 450}(7166), 63--70 Nov  (2007).

\bibitem{VaziriShank08}
Vaziri, A., Tang, J., Shroff, H., and Shank, C.~V.
\newblock {\em Proc Natl Acad Sci U S A}{ \bf 105}(51), 20221--20226 Dec
  (2008).

\bibitem{HelmstaedterDenk08}
Helmstaedter, M., Briggman, K.~L., and Denk, W.
\newblock {\em Curr Opin Neurobiol}{ \bf 18}(6), 633--641 Dec  (2008).

\bibitem{BuckinghamSattelle08}
Buckingham, S.~D. and Sattelle, D.~B.
\newblock {\em Invert Neurosci}{ \bf 8}(3), 121--131 Sep  (2008).

@@

\begin{figure}[h!]
% \centering 
\includegraphics[width=.5\linewidth]{Lhatplot}
\caption{C.~elegans graph classification simulation results. $\hL^{1000}_{F}(g_n)$ is plotted as a function of class-conditional training sample size $n_j$, suggesting that for $\varepsilon=0.1$ we can determine that $\MeB$ holds with $99\%$ confidence with just a few hundred training samples generated from $F_{BM}$. Each dot depicts an estimate for $L_{F}(g_n)$; standard errors are $(L_{F}(g_n)(1-L_{F}(g_n))/1000)^{1/2}$. E.g., $n_j = 180$ ; $k_n = 53$ ; $\hL^{1000}_{F}(g_n) = 0.057$; standard error less than 0.01. We reject $H_0: L_{F}(g^*) \geq 0.10$ at $\alpha=0.01$. $L_{F}(g^*) \approx 0$ for this simulation.
}
\label{fig1}
\end{figure}

>>>>

\author{Joshua T. Vogelstein\affil{1}{Johns Hopkins University, Baltimore, MD}, 
R. Jacob Vogelstein\affil{1}{}\affil{2}{Johns Hopkins University Applied Physics Laboratory, Laurel, MD}, 
Carey E. Priebe\affil{1}{}}

@@

\begin{acknowledgments}
The authors would like to acknowledge helpful discussions with J Lande, A Vaziri, and B Vogelstein. This work was supported in part by the NSA Research Program in Applied Neuroscience.
\end{acknowledgments}

@@

\begin{thebibliography}{10}

\bibitem{Plato97}
Plato, {\em Plato: complete works}.
\newblock Hackett Pub Co, 1997.

\bibitem{Descartes1641}
R.~Descartes, {\em Meditationes de prima philosophia}.
\newblock 1641.

\bibitem{Davidson70}
D.~Davidson, {\em Experience and Theory}, ch.~Mental Events.
\newblock Duckworth, 1970.

\bibitem{SpornsKotter05}
O.~Sporns, G.~Tononi, and R.~Kotter, ``The human connectome: A structural
  description of the human brain,'' {\em PLoS Computational Biology}, vol.~1,
  no.~4, p.~e42, 2005.

\bibitem{LichtmanSanes08}
J.~W. Lichtman, J.~Livet, and J.~R. Sanes, ``A technicolour approach to the
  connectome.,'' {\em Nat Rev Neurosci}, vol.~9, pp.~417--422, Jun 2008.

\bibitem{Seung09}
H.~Seung, ``{Reading the Book of Memory: Sparse Sampling versus Dense Mapping
  of Connectomes},'' {\em Neuron}, vol.~62, no.~1, pp.~17--29, 2009.

\bibitem{Kim95}
J.~Kim, {\em Phiilosophy of Mind}.
\newblock Westview Press, second~ed., 2005.

\bibitem{DGL96}
L.~Devroye, L.~Gy{\"o}rfi, and G.~Lugosi, {\em {A Probabilistic Theory of
  Pattern Recognition}}.
\newblock Springer, 1996.

\bibitem{Devroye83}
L.~Devroye, ``{On arbitrarily slow rates of global convergence in density
  estimation},'' {\em Probability Theory and Related Fields}, vol.~62, no.~4,
  pp.~475--483, 1983.

\bibitem{Popper}
K.~Popper, ``{The logic of scientific discovery},'' 1959.

\bibitem{WhiteBrenner86}
J.~White, E.~Southgate, J.~N. Thomson, and S.~Brenner, ``The structure of the
  nervous system of the nematode caenorhabditis elegans.,'' {\em Philosophical
  Transactions of Royal Society London. Series B, Biological Sciences},
  vol.~314, no.~1165, pp.~1--340, 1986.

\bibitem{DenkHorstmann04}
W.~W.~Denk and H.~Horstmann, ``Serial block-face scanning electron microscopy
  to reconstruct three-dimensional tissue nanostructure,'' {\em PLOS Biol.},
  vol.~2, p.~e329, 2004.

\bibitem{BriggmanDenk06}
K.~Briggman and W.~Denk, ``{Towards neural circuit reconstruction with volume
  electron microscopy techniques},'' {\em Current opinion in neurobiology},
  vol.~16, no.~5, pp.~562--570, 2006.

\bibitem{MackeBorst08}
J.~H. Macke, N.~Maack, R.~Gupta, W.~Denk, B.~Schölkopf, and A.~Borst,
  ``Contour-propagation algorithms for semi-automated reconstruction of neural
  processes.,'' {\em J Neurosci Methods}, vol.~167, pp.~349--357, Jan 2008.

\bibitem{Mishchenko09}
Y.~Mishchenko, ``Automation of 3d reconstruction of neural tissue from large
  volume of conventional serial section transmission electron micrographs.,''
  {\em J Neurosci Methods}, vol.~176, pp.~276--289, Jan 2009.

\bibitem{LuLichtman09}
J.~Lu, J.~C. Fiala, and J.~W. Lichtman, ``Semi-automated reconstruction of
  neural processes from large numbers of fluorescence images,'' {\em PLoS ONE},
  vol.~4, p.~e5655, 05 2009.

\bibitem{HornJohnson90}
R.~Horn and C.~Johnson, {\em {Matrix analysis}}.
\newblock Cambridge Univ Pr, 1990.

\bibitem{ConroyLouis97}
J.~M. Conroy, S.~G. Kratzer, and L.~J. Podrazik, ``A continuous method for the
  quadratic assignment problem,'' in {\em Society for Industrial and Applied
  Mathematics}, 1997.

\bibitem{ZaslavskiyVert08}
M.~Zaslavskiy, F.~Bach, and J.~Vert, ``{A path following algorithm for the
  graph matching problem},'' {\em IEEE Transactions on Pattern Analysis and
  Machine Intelligence}, vol.~31, pp.~2227--2242, 2008.

\bibitem{Durbin87}
R.~M. Durbin, {\em Studies on the Development and Organisation of the Nervous
  System of Caenorhabditis elegans}.
\newblock PhD thesis, University of Cambridge, 1987.

\bibitem{deBonoMaricq05}
M.~de~Bono and A.~V. Maricq, ``Neuronal substrates of complex behaviors in c.
  elegans.,'' {\em Annu Rev Neurosci}, vol.~28, pp.~451--501, 2005.

\bibitem{VarshneyChklovskii09}
L.~Varshney, B.~Chen, E.~Paniagua, D.~Hall, and D.~Chklovskii, ``{Structural
  Properties of the Caenorhabditis elegans Neuronal Network},'' {\em ArXiv},
  2009.

\bibitem{ChalasaniBargmann07}
S.~H. Chalasani, N.~Chronis, M.~Tsunozaki, J.~M. Gray, D.~Ramot, M.~B. Goodman,
  and C.~I. Bargmann, ``Dissecting a circuit for olfactory behaviour in
  caenorhabditis elegans.,'' {\em Nature}, vol.~450, pp.~63--70, Nov 2007.

\bibitem{VaziriShank08}
A.~Vaziri, J.~Tang, H.~Shroff, and C.~V. Shank, ``Multilayer three-dimensional
  super resolution imaging of thick biological samples.,'' {\em Proc Natl Acad
  Sci U S A}, vol.~105, pp.~20221--20226, Dec 2008.

\bibitem{HelmstaedterDenk08}
M.~Helmstaedter, K.~L. Briggman, and W.~Denk, ``3d structural imaging of the
  brain with photons and electrons.,'' {\em Curr Opin Neurobiol}, vol.~18,
  pp.~633--641, Dec 2008.

\bibitem{BuckinghamSattelle08}
S.~D. Buckingham and D.~B. Sattelle, ``Strategies for automated analysis of c.
  elegans locomotion.,'' {\em Invert Neurosci}, vol.~8, pp.~121--131, Sep 2008.

@@

\begin{figure}[h!]
% \centering 
% \includegraphics[width=.5\linewidth]{Lhatplot}
\caption{C.~elegans graph classification simulation results. $\hL^{1000}_{F}(g_n)$ is plotted as a function of class-conditional training sample size $n_j$, suggesting that for $\varepsilon=0.1$ we can determine that $\MeB$ holds with $99\%$ confidence with just a few hundred training samples generated from $F_{BM}$. Each dot depicts an estimate for $L_{F}(g_n)$; standard errors are $(L_{F}(g_n)(1-L_{F}(g_n))/1000)^{1/2}$. E.g., $n_j = 180$ ; $k_n = 53$ ; $\hL^{1000}_{F}(g_n) = 0.057$; standard error less than 0.01. We reject $H_0: L_{F}(g^*) \geq 0.10$ at $\alpha=0.01$. $L_{F}(g^*) \approx 0$ for this simulation.}
\label{fig1}
\end{figure}

### 2010-08-17 PNAS/cover_letter.tex
got reviews back from plos one, rearranged a bit and started making edits

\oddsidemargin=.2in
\evensidemargin=.2in
\textwidth=5.9in
\topmargin=-.5in
\textheight=9in

\name{	Joshua T.\ Vogelstein \\ 
		Johns Hopkins University \\
		Ph.D.\ Candidate in the Dept.\ of Neuro. \\
		% Postdoc.\ at Nat'l Center of Applied Neuro. \\
		% and the Department of Applied Mathematics and Statistics \\
		3400 N.\ Charles St.\ \\
		Krieger Hall, Rm.\ 338 \\
		Baltimore, MD 21205 \\
      	(443) 858-9911}

@@

\begin{letter}{	Prof.\ Gerald Edelman, M.D.\, Ph.D.\ \\
               	Chairman,The Scripps Research Institute \\
				10550 N.\ Torrey Pines Rd.\ \\
               	La Jolla, CA  92037-1000}

\opening{Dear Professor Edelman:}

On behalf of myself and my coauthors, I submit for your review a copy of our
manuscript entitled, ``Are mental properties supervenient on brain properties?''
We hope that you will consider ``communicating'' this manuscript to the
prestigious Proceedings of the National Academy of Sciences (PNAS).

@@

%Rather, it seems the typical approach is to first \emph{assume} such
%a relationship exists, and then find the \emph{location} of that relationship
%(to make a crude analogy, much of contemporary neuroscience seems to have taken
%a lesson from Decartes, who, assuming a relationship between an immaterial soul,
%and the body, found that the pineal gland was the location).

In addition to the philosophical implications, our work has significant
statistical implications.  Whereas several groups have recently proposed
algorithms for classifying graphs, there exists very little theoretical work on
the limitations of these tools.  In contrast, our work is founded on an
existance proof of a universally consistent classifier on graphs, the
limitations of which are both known and well-understood.  Although we only apply
this classifier to simulated brain-derived graphs, the methods are applicable to
many other kinds of graphical data. The recent emergence of networks and graphs 
as the preferred representations of structured relationships in multiple
scientific disciplines suggests that the development of statistical tools for
rigorous analysis of network data is a pressing need for the scientific
community at large.  
%Furthermore, we show using the arbitrarily slow convergence
%theorems, that only a one-sided result is possible, i.e., while we can be
%$100(1-\alpha)\%$ confident of the relationship between the properties under
%investigation, we can \emph{never} be confident in its negation.  This result
%is widely applicable outside the investigation of mind-brain supervenience.

@@

In summary, we believe that the work described in this manuscript makes
significant contributions in several contemporary fields of inquiry, and is
therefore suited for a general-audience peer-reviewed journal such as PNAS.  Your
interest in the philosophical underpinnings of neuroscience, as well as in
inferring causal relationships from neural data and generating large-scale
simulations of neural populations suggests to us that this manuscript would of
interest to you.  Please do not hesitate to contact us with any questions or
comments.

>>>>

\oddsidemargin=.2in
\evensidemargin=.2in
\textwidth=6in
\topmargin=-1.2in
\textheight=10in

\name{	Joshua T.\ Vogelstein, PhD. \\ 
		Johns Hopkins University \\
		% Ph.D.\ Candidate in the Dept.\ of Neuro. \\
		% Postdoc., 
		Dept. Applied Math.\ \& Stat's \\
		3400 N.\ Charles St.\ \\
		Barton 320 \\
		Baltimore, MD 21210 \\
      	(443) 858-9911}

@@

\begin{letter}{	%Prof.\ Gerald Edelman, M.D.\, Ph.D.\ \\
               	% Chairman,The Scripps Research Institute \\
               	% 10550 N.\ Torrey Pines Rd.\ \\
               	% La Jolla, CA  92037-1000
}

\opening{Dear Editorial Board:}

On behalf of myself and my coauthors, I submit for your review a copy of our manuscript entitled, ``Are mental properties supervenient on brain properties?'' We hope that you will consider publishing this manuscript to the prestigious Proceedings of the National Academy of Sciences (PNAS).

@@

In addition to the philosophical implications, our work has significant statistical implications. Whereas several groups have recently proposed algorithms for classifying graphs, there exists very little theoretical work on the limitations of these tools. In contrast, our work is founded on an existence proof of a universally consistent classifier on graphs, the limitations of which are both known and well-understood. Although we only apply this classifier to simulated brain-derived graphs, the methods are applicable to many other kinds of graphical data. The recent emergence of networks and graphs as the preferred representations of structured relationships in multiple scientific disciplines suggests that the development of statistical tools for rigorous analysis of network data is a pressing need for the scientific community at large.

@@

In summary, we believe that the work described in this manuscript makes significant contributions in several contemporary fields of inquiry, and is therefore suited for a general-audience peer-reviewed journal such as PNAS. %Your interest in the philosophical underpinnings of neuroscience, as well as in inferring causal relationships from neural data and generating large-scale simulations of neural populations suggests to us that this manuscript would of interest to you. 
Please do not hesitate to contact us with any questions or comments.
